---
title: "Demonstration of teachIRT Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{demonstration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",     # Center figures
  fig.width = 6,           # Width in inches (wider format)
  fig.height = 4,           # Height in inches
  dpi = 300,                # High-resolution output
  out.width = "80%"        # Ensure full width in HTML/PDF
)

```

teachIRT is an R package that can be used to teach and explore Item Response Theory (IRT). This vignette demonstrates how to install the package, provides an overview of all user functions included in the package, and includes exemplary code snippets for all functions.

## Installing the package

teachIRT can be installed from GitHub using the devtools package. If you haven't installed the devtools package yet, just run this code snippet:

```{r, eval = FALSE}
install.packages("devtools")
```

After installing the devtools package, the function devtools::install_github becomes available. It can be used to install a package from a GitHub repository. For the teachIRT package, the following command can be used:

```{r, eval = FALSE}
devtools::install_github("jkillisch/teachIRT")
```

If you would like to knit vignettes upon installation, you can use the following command:

```{r, eval = FALSE}
devtools::install_github(
  "jkillisch/teachIRT",
  build_vignettes = TRUE,
  dependencies = TRUE
)
```

Note, that teachIRT is not available on CRAN. So simply running install.packages("teachIRT") will result in an error message or an installation of the wrong package.

The current package version hosted on GitHub will always be checked on the latest version of MacOS, Windows and Ubuntu (release, developer, odrel-1) via GitHub Actions. On the package's GitHub page, there is a badge labelled R-CMD-check.yaml. If the badge is marked as *passed*, the package should install on these systems. If you, nevertheless, encounter problems while installing the package, please don't hesitate sending an email (see <https://github.com/jkillisch>).

After installing the package, it can be loaded just like any other R package:

```{r setup}
library(teachIRT)
```

## Overview of Functions Available in teachIRT

teachIRT provides five types of functions

(1) **Functions to compute probabilities**, e.g. probabilities to solve an item or to respond in a certain category. These functions begin with a p\_ followed by the model name.

(2) **Functions to plot probabilities** (ICCs, OCCs, CCCs). These functions begin with the type of plot followed by the model name.

(3) **Functions to compute measures of statistical information**. These functions begin with an inf\_ followed by the model name. These functions are, currently, only available for the 1PL-3PL model.

(4) **Functions to plot measures of statistical information**. These functions begin with an inf_plot\_ followed by the model name.

(5) **Functions to compute confidence intervals around person parameters**. These functions begin with a ci\_ followed by the model name. These functions are, currently, only available for the 1PL-3PL model.

(6) **Functions to simulate responses**. These functions begin with a sim\_ followed by the model name. These functions are available for all rating scale models.

The model names are rasch, 2pl, 3pl, pcm, gpcm, grm, and tirt. The following table displays all functions by model and function type.

+------------+-------------+------------------+-------------+------------------+---------------------+------------+
| Model      | Probability | Probability Plot | Information | Information Plot | Confidence Interval | Simulation |
+============+=============+==================+=============+==================+=====================+============+
| 1PL/ Rasch | p_rasch     | icc_rasch        | inf_rasch   | inf_plot_rasch   | ci_rasch            | sim_rasch  |
+------------+-------------+------------------+-------------+------------------+---------------------+------------+
| 2PL        | p_2pl       | icc_2pl          | inf_2pl     | inf_plot_2pl     | ci_2pl              | sim_2pl    |
+------------+-------------+------------------+-------------+------------------+---------------------+------------+
| 3PL        | p_3pl       | icc_3pl          | inf_3pl     | inf_plot_3pl     | ci_3pl              | sim_3pl    |
+------------+-------------+------------------+-------------+------------------+---------------------+------------+
| PCM        | p_pcm       | icc_pcm          |             |                  |                     | sim_pcm    |
+------------+-------------+------------------+-------------+------------------+---------------------+------------+
| GPCM       | p_gpcm      | icc_gpcm         |             |                  |                     | sim_gpcm   |
+------------+-------------+------------------+-------------+------------------+---------------------+------------+
| GRM        | p_grm       | occ_grm          |             |                  |                     | sim_grm    |
|            |             |                  |             |                  |                     |            |
|            |             | ccc_grm          |             |                  |                     |            |
+------------+-------------+------------------+-------------+------------------+---------------------+------------+
| TIRT       | p_tirt      | icc_tirt         |             |                  |                     |            |
+------------+-------------+------------------+-------------+------------------+---------------------+------------+

All functions displayed in the table come with a help file. If the package has been loaded, it can be shown by typing a question mark followed by the function name, e.g.:

```{r}
?icc_2pl
```

## Demonstration of Functions Available in teachIRT

### Rasch-Model

```{r}
# Probability to solve an item
p_rasch(theta = 3, beta = 2)
p_rasch(theta = 4, beta = 2)
p_rasch(theta = 2, beta = 3)

# Plot an ICC
icc_rasch(beta = -0.7)

# Wider x-axis
icc_rasch(theta_range = c(-10, 10), beta = -0.7)

# Multiple items (currently only for 1PL-3PL ICCs)
icc_rasch(beta = -1:1)

# Information at theta
inf_rasch(theta = 0.5, beta = 0.4)

# Plot information function
inf_plot_rasch(beta = 0.5)

# Compute confidence interval around theta using test information
ci_rasch(
  theta = 0,
  beta = c(-0.5, 0, 1.2),
  ci_alpha = 0.05,
  ci_direction = "both"
)

# Simulate responses
sim_rasch(10, 5)
```

### 2PL-Model

```{r}
# Probability to solve an item
p_2pl(theta = 1.5, beta = 0.5, alpha = 1)
p_2pl(theta = 1, beta = 0.5, alpha = 1)
p_2pl(theta = 1.5, beta = 0.5, alpha = 0.2)
p_2pl(theta = 1, beta = 0.5, alpha = 0.2)

# Plot ICC of an item
icc_2pl(alpha = 1.2, beta = 1.5)

# Plot ICCs of multiple items
icc_2pl(alpha = c(1, 1.2), beta = c(0, 1.5))

# Information at theta
inf_2pl(theta = 0.5, alpha = 1.2, beta = 1.5)

# Plot information function
inf_plot_2pl(alpha = 1.2, beta = 1.5)

# You can manually scale the y-axis for better comparisons
inf_plot_2pl(alpha = 1.2, beta = 1.5, y_lim = 1)

# Compute confidence interval around theta using test information
ci_2pl(
  theta = 0,
  beta = c(-0.5, 0, 1.2),
  alpha = c(0.5, 1.2, 0.1),
  ci_alpha = 0.05,
  ci_direction = "both"
)

# Simulate responses
sim_2pl(10, 5)
```

### 3PL-Model

```{r}
# Probability to solve an item
p_3pl(theta = -5, beta = 0.5, alpha = 1, gamma = 0.3)

# Plot ICC of an item
icc_3pl(alpha = 1, beta = 0.5, gamma = 0.3)

# Plot ICCs of multiple items
icc_3pl(alpha = c(0.5, 1), beta = c(1, 0.5), gamma = c(0.2, 0.3))

# Information at theta
inf_3pl(theta = 0, alpha = 1, beta = 0.5, gamma = 0.3)

# Plot information function
inf_plot_3pl(alpha = 1, beta = 0.5, gamma = 0.3)

# Compute confidence interval around theta using test information
ci_3pl(
  theta = 0,
  beta = c(-0.5, 0, 1.2),
  alpha = c(0.5, 1.2, 0.1),
  gamma = c(0, 0.2, 0.4),
  ci_alpha = 0.05,
  ci_direction = "both"
)

# Simulate responses
sim_3pl(10, 5)
```

### Partial Credit Model

```{r}
# Compute category probabilities
p_pcm(theta = 0.5, delta = c(-1, 0, 1))

# Plot ICCs of an item
icc_pcm(delta = c(-1, 0, 1))

# Simulate responses
sim_pcm(10, 5, 3)
```

### Generalized Partial Credit Model

```{r}
# Compute categoriy probabilities
p_gpcm(theta = 0, alpha = 2, delta = c(-3, -1, 2))

# Plot ICC of an item
icc_gpcm(alpha = 2, delta = c(-3, -1, 2))

# Simulate responses
sim_gpcm(10, 5, 3)
```

### Graded Response Model

```{r}
# Compute step probabilities
p_step_grm(theta = 1, delta = c(-2, -0.5, 1.5), alpha = 1.2)

# Compute category probabilities
p_grm(theta = 1, delta = c(-2, -0.5, 1.5), alpha = 1.2)

# Plot OCCs of an item
occ_grm(alpha = 1.2, delta = c(-2, -0.5, 1.5))

# Plot CCCs of an item
ccc_grm(alpha = 1.2, delta = c(-2, -0.5, 1.5))

# Simulate responses
sim_grm(10, 5, 3)
```

### Thurstonian IRT Model

```{r}
# Plot probability of prefer item 1 over item 2 in a pair
p_tirt(
  theta = c(0.5, 0.7),
  mu = c(1, 0.3),
  lambda = c(0.74, 0.4),
  psi2 = c(1, 1)
)

# Plot ICC of a pair
icc_tirt(
  mu = c(1, 0.3),
  lambda = c(0.74, 0.4),
  psi2 = c(1, 1),
  rotation = -40 # Change this number to rotate the plot
)
```
